---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# lmmtools

## A Set of Tools for Linear Mixed Models

```{r, echo = FALSE}
description <- read.dcf('DESCRIPTION')
version <- as.vector(description[, 'Version'])
min.r <- substr(description[,"Depends"], 21, 25)
```

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r min.r`-6666ff.svg)](https://cran.r-project.org/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r gsub('-', '--', version)`-orange.svg?style=flat-square)](https://github.com/biometryhub/lmmtools/commits/main)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](https://choosealicense.com/licenses/mit/)
<!-- badges: end -->

This package contains a range of functions useful either before an analysis using `ASReml-R`, or after fitting.

----

## Installation

<!-- ### Development version -->

<!-- ⚠ **Warning**: The development version is unstable and liable to change more often than the CRAN version. It may have bugs fixed, but there may be other currently unknown bugs introduced. ⚠ -->

Use the following code to install the latest version of this package.

```{r eval=F}
if(!require("pak")) install.packages("pak") 
pak::pak("biometryhub/lmmtools")
```


## Using the package

Load the package and start using it with:

```{r eval=F}
library(lmmtools)
```

## Note: Licencing ASReml-R

ASReml-R is a proprietary R package which is sold and supported by [VSN International](https://vsni.co.uk/), and requires a licence code to activate and run. This licence code is checked for validity via the internet, and may require opening some network ports on your computer to successfully activate. Further information about the licence requirements can be obtained from [VSNi directly](https://vsni.co.uk/licensing/).

The developers of lmmtools do not provide support for `ASReml-R` via way of bug reports or software patches, and any problems with the ASReml-R software should be directed to [VSN International](https://vsni.co.uk/). 

## Citing lmmtools

If you find this package useful, please cite it! Type `citation("lmmtools")` on the R console to find out how.
