---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# lmmtools

## A Set of Tools for Linear Mixed Models

```{r, echo = FALSE}
description <- read.dcf('DESCRIPTION')
version <- as.vector(description[, 'Version'])
min.r <- substr(description[,"Depends"], 7, 11)
```

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- [![Codecov test coverage](https://codecov.io/gh/biometryhub/biometryassist/branch/main/graph/badge.svg)](https://app.codecov.io/gh/biometryhub/biometryassist?branch=main) -->
<!-- [![R build status](https://github.com/biometryhub/biometryassist/workflows/R-CMD-check/badge.svg)](https://github.com/biometryhub/biometryassist/actions) -->
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r min.r`-6666ff.svg)](https://cran.r-project.org/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r gsub('-', '--', version)`-orange.svg?style=flat-square)](https://github.com/biometryhub/biometryassist/commits/main)
[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](https://choosealicense.com/licenses/mit/)
[![Hits](https://hits.seeyoufarm.com/api/count/incr/badge.svg?url=https%3A%2F%2Fgithub.com%2Fbiometryhub%2Flmmtools&count_bg=%2379C83D&title_bg=%23555555&icon=&icon_color=%23E7E7E7&title=hits&edge_flat=false)](https://hits.seeyoufarm.com)
<!-- badges: end -->

This package conatins a range of functions useful either before an analysis using asreml-R, or after fitting.

----

## Installation

<!-- ### Development version -->

<!-- ⚠ **Warning**: The development version is unstable and liable to change more often than the CRAN version. It may have bugs fixed, but there may be other currently unknown bugs introduced. ⚠ -->

Use the following code to install the latest version of this package.

```{r eval=F}
if(!require("remotes")) install.packages("remotes") 
remotes::install_github("biometryhub/lmmtools")
```


## Using the package

Load the package and start using it with:

```{r eval=F}
library(lmmtools)
```

If you find this package useful, please cite it! Type `citation("lmmtools")` on the R console to find out how.
